Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-02 method.tex
Made number of signal parameters explicit
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@848 ccdd05d5-56c1-461a-bf98-85f6876523b4

Inspiral signals are continuously parameterized by a set of intrinsic source parameters
$\vec\theta$ that determine the amplitude and phase evolution of the gravitational wave strain. For systems where the effects of spin can be ignored, the
intrinsic source parameters are the component masses of the binary, $\vec\theta =
(m_1, m_2)$. Searches for inspiral signals
typically employ matched filter banks that discretely
sample the possible intrinsic parameters~\cite{findchirppaper}.  For a given source, the strain observed by the detector is a linear combination of two waveforms corresponding to the `$+$' and `$\times$' gravitational wave polarizations, so for any value of $\vec\theta$ we must implement 2 filters.  The coefficients for the $M$ filters
are known as templates, and are formed by discretizing and time reversing the waveforms and weighting them by the inverse amplitude spectral density of the detector's noise. To construct a template bank, templates are chosen with discrete signal parameters $\vec\theta_0,\, \vec\theta_1,\, \dots,\, \vec\theta_{M/2-1}$ to assure a
bounded loss of \SNR~\cite{Owen:1995tm,Owen:1998dk}. That is, any possible
signal within the a given range of intrinsic source parameters will have an inner product that is $\geqslant 0.97$ with
at least one template. Such a template bank is said to have a {\em
minimum match} of 0.97. The data from the detector are whitened and convolved with each template to produce $2M$ \SNR\
time series. Local peak-finding across time and templates determines detection
candidates.

>>>>

Inspiral signals are continuously parameterized by a set of intrinsic source parameters
$\vec\theta$ that determine the amplitude and phase evolution of the gravitational wave strain. For systems where the effects of spin can be ignored, the
intrinsic source parameters are the component masses of the binary, $\vec\theta =
(m_1, m_2)$. Searches for inspiral signals
typically employ matched filter banks that discretely
sample the possible intrinsic parameters~\cite{findchirppaper}.  For a given source, the strain observed by the detector is a linear combination of two waveforms corresponding to the `$+$' and `$\times$' gravitational wave polarizations, so for any value of $\vec\theta$ we must implement 2 filters.  The coefficients for the $M$ filters
are known as templates, and are formed by discretizing and time reversing the waveforms and weighting them by the inverse amplitude spectral density of the detector's noise. To construct a template bank, templates are chosen with the $M/2$ discrete signal parameters $\vec\theta_0,\, \vec\theta_1,\, \dots,\, \vec\theta_{M/2-1}$ to assure a
bounded loss of \SNR~\cite{Owen:1995tm,Owen:1998dk}. That is, any possible
signal within the a given range of intrinsic source parameters will have an inner product that is $\geqslant 0.97$ with
at least one template. Such a template bank is said to have a {\em
minimum match} of 0.97. The data from the detector are whitened and convolved with each template to produce $2M$ \SNR\
time series. Local peak-finding across time and templates determines detection
candidates.
